---
title: "Performance of image decomposition"
author: "Alejandro Pulver"
date: "05/01/2014"
output: html_document
---

```{r, message=FALSE}
library(ggplot2)
library(plyr)
#library(timeit)
#library(pander)
source("utils.R")
```

In this article we'll compare the performance of many SVD/eigen decomposition algorithms for greyscale images. They may perform very differently for more rectangular or sparse matrices, for example.

```{r, echo=FALSE, message=FALSE}
# SVD libraries
library(corpcor)
library(irlba)
library(QZ)
library(rARPACK)
library(svd)

methods = list(
  list(name = "eigen", func = function(m, nc) {
    eigen(m %*% t(m))
  }),
  list(name = "svd", func = function(m, nc) {
    svd(m, nu=nc, nv=nc)
  }),
  list(name = "fast.svd", func = function(m, nc) {
    fast.svd(m)
  }),
  list(name = "irlba", func = function(m, nc) {
    irlba(m, nu=nc, nv=nc)
  }),
  list(name = "QZ", func = function(m, nc) {
    geigen(m %*% t(m))
  }),
  list(name = "rARPACK", func = function(m, nc) {
    svds(m, nc)
  }),
  list(name = "propack", func = function(m, nc) {
    propack.svd(m, nc)
  }),
  list(name = "trlan", func = function(m, nc) {
    trlan.svd(m, nc)
  })
)
```

We have a `images` folder with a few files, and a list of algorithms. For all possible combinations, a time will be calculated.

```{r, cache=TRUE}
imageFiles <- dir("images")

svdTimes <- ldply(imageFiles, function(imgName) {
  imgRGB <- my.readImage(sprintf("images/%s", imgName))
  img <- my.rgb2grey(imgRGB)
  
  ldply(methods, function(alg) {  
    prof <- system.time({alg$func(img, 100)})
    #time <- prof[["user.self"]] + prof[["user.child"]]
    time <- prof[["elapsed"]]
    
    data.frame(image=imgName, method=alg$name, time=time)
  })
})

save(svdTimes, file="svdTimes.Rda")
```

And here are the results, note that **eigen** and **QZ** obtain all singular values because they operate on `m*t(m)`. The rest were asked for the 100 largest ones.

```{r, fig.width=10, fig.height=7}
load("svdTimes.Rda")
df <- svdTimes[svdTimes$method != "QZ",]
ggplot(df, aes(x=method, y=time)) + geom_boxplot() + geom_jitter()
```